---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
1A Load Data
```{r LoadData, echo = TRUE}
library(lattice)
library(knitr)
data=read.csv("M:/Courses/datasciencecoursera/RR/RepData_PeerAssessment1/activity.csv", header = TRUE )
summary(data)
```

1B Process/Transform data

- We need to remove incomplete rows from the dataset.

```{r TranformData, echo = TRUE}
data2 = data
data2_without_NA <-data2[complete.cases(data2),]
NA_num <- nrow(data2) - nrow(data2_without_NA)
```

- To calculate the minimum and maximum date we need to convert to "Data" type.  

```{r date conversion, echo = TRUE}
min_date <- min(as.Date(data2$date)) 
max_date <- max(as.Date(data2$date))
tcd <-as.numeric(max_date- min_date) +1
```

## What is mean total number of steps taken per day?
Calculate nr of steps per day
```{r calcsteps, echo = TRUE}
tsd_day <-as.data.frame(tapply(data2_without_NA$steps, INDEX = data2_without_NA$date, FUN = "sum", na.rm = TRUE))
colnames(tsd_day)<-"steps"
tsd_day$date <- as.Date(rownames(tsd_day))
tsd_day$steps <- as.integer(tsd_day$steps)
```

Draw the histogram with frequency of total number of steps per day

```{r histogram, echo = TRUE}
hist(tsd_day$steps, main = "Total nr of Steps per day without NA", xlab = "Total nr of steps per day", ylab = "Frequency (nr of days)", breaks = 10, xlim = c(0,25000), ylim = c(0,25), col = "blue")
```

Calculate mean and median
```{r mean, echo = TRUE}
mean_without_NA <- mean(tsd_day$steps, na.rm = TRUE)
median_without_NA <- median(tsd_day$steps, na.rm = TRUE)
```

With missing values removed the mean for total number of steps per day is  `r mean_without_NA`.

With missing values removed the median for total number of steps per day is  `r median_without_NA`.


## What is the average daily activity pattern?



## Imputing missing values
```{r nrow, echo = TRUE}
NA_num <- nrow(data2) - nrow(data2_without_NA)
```
A. There are `r NA_num` NA recs out of `r nrow(data2)` total recs.



## Are there differences in activity patterns between weekdays and weekends?
